|

### 2019-09-23 paper.Rmd
Reference appendix in paper.
Fixing acknowledgements.

The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr]. The source material for this paper are available at \url{https://github.com/uschiLaa/paper-slice-tour} and animated gifs can be found at \url{https://uschilaa.github.io/paper-slice-tour/}.

>>>>

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr]. The source material and animated gifs for this paper are available at \url{https://github.com/uschiLaa/paper-slice-tour}. An appendix deriving the relative slice volume for the hypersphere is included as supplemental material.
